Native advertising as a content marketing strategy

### 2024-08-26 analysis/paper/paper.Rmd
los

Application area: Is native advertising a public relations technique, a marketing tool, or a tactic that does not differ from traditional advertising in any way?

Authorship of native ads: Who creatively signs them and who is responsible for their content?
Legal and ethical framework: How is native advertising legally defined, and what is the practice of media houses in labeling such advertisements (Trbušić, Maleš & Šikić, 2024).

@@

The goal of the research is to determine the basic characteristics of the content elements of native ads (as one of the strategies of content marketing) on ​​the observed most read Croatian internet portals. The specific objectives of the research are focused on the observation of two broader entities. It is about the features of the title (e.g. types of sentences in the titles, representation and types of clickbait titles, mention of the brand name) and the analysis of elements within the content of native ads (e.g. citing sources, i.e. use of interlocutor statements, use of equipment and visual identity). The mentioned categories were not chosen arbitrarily, but were defined according to the types and typology of content marketing (see p. 5). In addition, the goal is to determine whether there is a significant correlation between the characteristics of the title and content of native ads with audience reach. Equally, attention is also focused in the work on the specifics that are observed in this type of advertising in different industries, i.e. different practices resorted to by those ordering native ads.

@@

>>>>

> Application area: Is native advertising a public relations technique, a marketing tool, or a tactic that does not differ from traditional advertising in any way?

> Authorship of native ads: Who creatively signs them and who is responsible for their content?

> Legal and ethical framework: How is native advertising legally defined, and what is the practice of media houses in labeling such advertisements (Trbušić, Maleš & Šikić, 2024).

@@

The goal of the research is to determine the basic characteristics of the content elements of native ads (as one of the strategies of content marketing) on the observed most read Croatian internet portals. The specific objectives of the research are focused on the observation of two broader entities. It is about the features of the title (e.g. types of sentences in the titles, representation and types of clickbait titles, mention of the brand name) and the analysis of elements within the content of native ads (e.g. citing sources, i.e. use of interlocutor statements, use of equipment and visual identity). The mentioned categories were not chosen arbitrarily, but were defined according to the types and typology of content marketing (see p. 5). In addition, the goal is to determine whether there is a significant correlation between the characteristics of the title and content of native ads with audience reach. Equally, attention is also focused in the work on the specifics that are observed in this type of advertising in different industries, i.e. different practices resorted to by those ordering native ads.

@@

<details>
<summary>Click to expand the code chunk</summary>
```{r}

industry_list <- data.frame(
  id = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28),
  category = c(
    "Financijska industrija",
    "Građevinska industrija",
    "Moda i ljepota",
    "Politička institucija",
    "Sportska industrija",
    "Zdravstvena industrija",
    "Obrazovanje i znanost",
    "Tehnologija",
    "Auto-moto industrija",
    "ICT industrija",
    "Kultura i umjetnost",
    "Turizam, odmor, putovanja, ugostiteljstvo",
    "Energetska industrija",
    "Prehrambena industrija",
    "Industrija bezalkoholnih pića",
    "Alkoholna pića",
    "Industrija nekretnina",
    "Maloprodaja",
    "Igre na sreću",
    "Medijske kuće i marketinške, digitalne agencije",
    "Namještaj, saloni namještaja, kućanske potrepštine, kućanski uređaji, sredstva za čišćenje",
    "Trgovački / shopping centri",
    "Glazbena industrija",
    "Filmska industrija",
    "Brodogradnja",
    "Pošta / distribucija pošiljki",
    "Komunalne usluge"
  )
)

IND <- dta %>%
  group_by(INDUSTRIJA) %>%
  summarise(N = n()) %>% 
  mutate(percentIND = round(N / sum(N) * 100,2))

# Create a histogram of the 'price' variable in the 'diamonds' dataset
# ggplot(data = IND, aes(x = percentIND)) +
#   geom_histogram(binwidth = 1, fill = "blue", alpha = 0.7) +
#   ggtitle("Industrija") +
#   xlab("Industrija") +
#   ylab("%") +
#   scale_x_continuous(breaks = seq(from = min(dta$INDUSTRIJA), to =  max(dta$INDUSTRIJA), by = 1))

# Joining the dataframes
IND_joined <- IND %>%
  left_join(industry_list, by = c("INDUSTRIJA" = "id")) %>%
  arrange(desc(N))

# Reordering the levels of 'category'
IND_joined$category <- with(IND_joined, reorder(category, percentIND))

#Plotting
ggplot(data = IND_joined, aes(x = category, y = percentIND)) +
  geom_bar(stat = "identity", fill = "black") +
  labs(title = "Industrija", x = "Industrija", y = "%") +
  theme_minimal() +
  # theme(
  #   axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
  #   panel.grid.major.x = element_blank(),  # Remove vertical grid lines
  #   panel.border = element_rect(fill = NA, color = "black")  # Add border
  # ) +
  coord_flip()  # Flip coordinates to have horizontal bars

# IND %>%
#   datatable(., options = list(scrollX = TRUE, scrollY = "500px"))
# 
# 
# industry_list %>%
#   datatable(., options = list(scrollX = TRUE, scrollY = "500px"))

IND_joined <- IND %>%
  left_join(industry_list, by = c("INDUSTRIJA" = "id"))

IND_final <- IND_joined %>%
  select(category, N, percentIND) %>%
  arrange(desc(N))

IND_kable <- IND_final %>%
  kable(format = "html", 
        col.names = c("Industrija", "Broj objava", "%"),
        caption = "Pregled po industrijama") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

IND_kable

```{r echo=F, eval=T, message=F , warning= FALSE}
IND_kable
```

```{r echo=F, eval=T, message=F , warning= FALSE}
# Portals by reach
reach <- dta %>%
  group_by(FROM) %>%
  summarise(reach = sum(REACH)) %>%
  arrange(desc(reach))

reach

# make detailed descriptive statistics

summary(dta$REACH)

filtered_dta <- dta %>% filter(REACH >= 0 & REACH <= 30000)

# Create the histogram
hist(filtered_dta$REACH, 
     xlab = "Reach", 
     ylab = "Frequency", 
     main = "Reach of Portals", 
     col = "blue", 
     breaks = 50)
